Object-Oriented Internet\\ Cloud Interoperability

### 2021-01-09 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Apply LLNCS formatting and rules #52
- llncsdoc.pdf has been applied

\title{Object-Oriented Internet\\ Cloud Interoperability}
\titlerunning{OOI - Cloud Interoperability}

\author{Mariusz Postół\inst{1}\orcidID{0000-0002-9669-0565}  \and Piotr Szymczak\inst{1}\orcidID{0000-0001-6790-3878} }
\authorrunning{M. Postół et al.}

@@

      \keywords{Industry 4.0 \and Internet of Things \and Object-Oriented Internet \and Cloud Computing \and Industrial communication \and Reactive Networking (RxNetworking)\and Machine to Machine Communication \and OPC Unified Architecture \and Azure}

@@

Unlike the above-described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept. A generic domain model for this interconnection is presented in the Fig.~\ref{figure1.StrategyDomainModel}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}. The main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

@@

\section{Azure - OOI Implementation}\label{section.gateway-implementation}

>>>>

\title{Object-Oriented Internet\\ Cloud Interoperability}
%\titlerunning{OOI - Cloud Interoperability}

\author{Mariusz Postół\inst{1}\orcidID{0000-0002-9669-0565}  \and Piotr Szymczak\inst{1}\orcidID{0000-0001-6790-3878} }
%\authorrunning{M. Postół et al.}

@@

      \keywords{Industry 4.0 \and Internet of Things \and Object-Oriented Internet \and Cloud Computing \and Industrial communication \and Reactive networking \and Machine to Machine Communication \and OPC Unified Architecture \and Azure}

@@

\begin{proposition}
Unlike the above-described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept. A generic domain model for this interconnection is presented in the Fig.~\ref{figure1.StrategyDomainModel}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}. The main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
\end{proposition}

@@

\section{Azure - OOI Interoperability Implementation}\label{section.gateway-implementation}
